---
title: "Palm trees in agroforestry"
author: "R. Vezy"
date: "17 avril 2019"
output:
  html_document: default
  github_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

The aim of this project is to simulate Palm oil trees in agroforestry.
The aim of the first project is to mix *Elaeis guineensis* trees with upland rice in collaboration with the Brawijaya university in Malang, Indonesia. 

This website is generated using the `make_website()` function as follows: 

```{r eval=FALSE}
source("helper-functions.R")
make_website()
```

## [*E. guineensis* and rice](palm_rice.html)

To simplify the simulations, we only simulate palm trees in the scene, and compute the light incident on a plane at 1 meter above the ground, i.e. at the height of the fully grown rice plants. More details about the project can be found in the Palm_Rice folder.

Please visit the [associated webpage](palm_rice.html) for further details.
